Cognate Priming

### 2022-12-21 docs/index.qmd
Stop ignoring HTMLs in the docs/ folder

```{r}
#| label: fig-stimuli-category-prime
#| fig-height: 7
#| fig-width: 12
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	drop_na(trial_type, semantic_category_prime) %>% 
	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(test_language~trial_type,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

@@

```{r}
#| label: fig-stimuli-category-target
#| fig-height: 7
#| fig-width: 12
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	drop_na(trial_type, semantic_category_target) %>% 
	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(test_language~trial_type,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

@@

```{r}
#| label: fig-vocabulary-l1
#| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
#| fig-height: 4
sample_size <- participants %>% 
	filter(id %in% fit_0$data$id) %>% 
	count(age_group)

@@

```{r}
#| label: fig-vocabulary-total
#| fig-cap: "Total vocabulary"
#| fig-height: 4
# vocabulary
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

```{r}
#| label: fig-vocabulary-conceptual
#| fig-height: 4
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

```{r}
#| label: fig-prior-epred
nd <- tibble(time_bin = seq(0, 20, 0.1)) %>% 
	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)

@@

	cols_label(n_excluded = "Excluded",
			   n_valid = "Included",
			   freq_prime_mean_valid = "Included",
			   freq_prime_mean_excluded = "Excluded",
			   freq_target_mean_valid = "Included",
			   freq_target_mean_excluded = "Excluded",
			   familiarity_prime_mean_valid = "Included",
			   familiarity_prime_mean_excluded = "Excluded",
			   familiarity_target_mean_valid = "Included",
			   familiarity_target_mean_excluded = "Excluded") %>% 
	summary_rows(groups = TRUE,
				 columns = matches("freq_") ,
				 fns = list("Mean" = ~mean(.)), 
				 formatter = fmt_number,
				 decimals = 1) %>% 
	summary_rows(groups = TRUE,
				 columns = matches("familiarity_"), 
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_number,
				 scale_by = 100,
				 decimals = 1) %>% 
	grand_summary_rows(columns = c(n_valid, n_excluded),
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	grand_summary_rows(columns = matches("familiarity_"),
					   fns = list("Mean" = ~mean(.)),
					   formatter = fmt_number,
					   scale_by = 100,
					   decimals = 1) %>% 
	grand_summary_rows(columns = matches("freq_"),
					   fns = list("Mean" = ~mean(.)),
					   formatter = fmt_number,
					   decimals = 1) %>% 
	tab_style(cell_text(align = "center"),
			  cells_column_labels()) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary()))

@@

```{r}
#| label: fig-descriptives-aggregated
df %>% 
	group_by(id, lp, trial_type, age_group) %>%
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_line(aes(group = id), alpha = 0.25) +
	stat_slab(side = "right", scale = 0.5) +
	geom_boxplot(width = 0.1, size = 0.75, fill = "white", colour = "black", outlier.colour = NA) +
	labs(x = "Trial type", y = "Proportion of target looking", colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
	theme(legend.position = "none")
```

@@

```{r}
#| label: fig-descriptives-time-course
df %>% 
	group_by(id, time_bin, lp, trial_type, age_group) %>%
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(time_bin, prop, colour = trial_type, fill = trial_type, shape = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
	stat_summary(fun = mean, geom = "point", size = 2) +
	stat_summary(fun = mean, geom = "line", size = 0.75) +
	labs(x = "Time bin (100 ms)", y = "Proportion of target looking",
		 colour = "Trial type", fill = "Trial type", shape = "Trial type") +
	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
	theme(legend.position = "top",
		  panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
```

@@

str_repl <- c(
	"b_Intercept" = "Base",
	"b_ot1" = "Base",
	"b_ot2" = "Base",
	"b_ot3" = "Base",
	"b_age_group21_25" = "Age [21-25]",
	"b_age_group25_30" = "Age [25-30]",
	"b_lpmon_bil" = "Group",
	"b_trial_typerelated_unrelated" = "Prime (relatedness)",
	"b_trial_typecognate_noncognate" = "Prime (cognateness)",

	"b_age_group21_25:lpmon_bil" = "Age [21-25] × Group",
	"b_age_group25_30:lpmon_bil" = "Age [25-30] × Group",
	"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (relatedness)",
	"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (cognateness)",
	"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (relatedness)",
	"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (cognateness)",
	"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (relatedness)",
	"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (cognateness)",

	"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (relatedness)",
	"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (cognateness)",
	"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (relatedness)",
	"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (cognateness)"
)

@@

```{r}
#| label: fig-posterior-epred
nd <- expand_grid(time_bin = seq(0, 20, 0.1),
				  age_group = levels(fit_1$data$age_group),
				  lp = levels(fit_2$data$lp),
				  trial_type = levels(fit_4$data$trial_type)) %>% 
	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)

>>>>

```{r}
#| label: fig-stimuli-category-prime
#| fig-height: 5
#| fig-width: 10
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	drop_na(trial_type, semantic_category_prime) %>% 
	count(trial_type, test_language, semantic_category_prime, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  semantic_category_prime)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category_prime, desc(prop), list(trial_type, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(test_language~trial_type,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

@@

```{r}
#| label: fig-stimuli-category-target
#| fig-height: 5
#| fig-width: 10
stimuli %>% 
	distinct(test_language,  target,  prime, .keep_all = TRUE) %>% 
	drop_na(trial_type, semantic_category_target) %>% 
	count(trial_type, test_language, semantic_category_target, name = "sum") %>% 
	right_join(expand(., trial_type,  test_language,  semantic_category_target)) %>%
	replace_na(list(sum = 0)) %>% 
	group_by(trial_type, test_language) %>% 
	mutate(n =  sum(sum), prop = sum/n) %>% 
	ungroup() %>% 
	ggplot() +
	aes(x = prop,
		y = reorder_within(semantic_category_target, desc(prop), list(trial_type, test_language)),
		fill = test_language,
		order = prop) + 
	facet_wrap(test_language~trial_type,
			   scales = "free_y",
			   labeller = label_wrap_gen(multi_line = FALSE)) +
	geom_col(colour = "white",
			 position = position_dodge(),
			 width = 1) +
	labs(x = "% of trials",
		 y = "Trial type",
		 colour = "Trial type",
		 fill = "Trial type") +
	scale_x_continuous(labels = ~percent(., accuracy = 1)) +
	scale_y_reordered() +
	theme(legend.position = "none",
		  legend.title = element_blank(),
		  axis.text.y = element_text(size = 9, hjust = 1),
		  axis.text.x = element_text(size = 8, hjust = 1),
		  axis.title.y = element_blank(),
		  axis.ticks.y = element_blank(),
		  plot.caption = element_text(size = 10, hjust = 0),
		  panel.grid.major.x = element_line(colour = "grey", linetype = "dotted"),
		  strip.text = element_text(size = 10))
```

@@

```{r}
#| label: fig-vocabulary-l1
#| fig-cap: "L1 vocabulary. Percentage of words in L1 reported to be understood from the vocabulary checklist."
#| fig-height: 5
#| fig-width: 8
sample_size <- participants %>% 
	filter(id %in% fit_0$data$id) %>% 
	count(age_group)

@@

```{r}
#| label: fig-vocabulary-total
#| fig-cap: "Total vocabulary"
#| fig-height: 5
#| fig-width: 8
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_total, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

```{r}
#| label: fig-vocabulary-conceptual
#| fig-height: 5
#| fig-width: 8
participants %>% 
	mutate(
		age_group = case_when(
			age_group=="21 months" ~ paste0(age_group, " (N = ", sample_size$n[1], ")"),
			age_group=="25 months" ~ paste0(age_group, " (N = ", sample_size$n[2], ")"),
			age_group=="30 months" ~ paste0(age_group, " (N = ", sample_size$n[3], ")")
		),
		is_imputed = factor(ifelse(is_imputed, "Imputed", "Observed"),
							levels = c("Observed", "Imputed"))
	) %>% 
	drop_na(lp) %>%
	filter(valid_participant) %>% 
	ggplot(aes(lp,  vocab_size_conceptual, colour = is_imputed, fill = is_imputed)) +
	facet_wrap(~age_group, scales = "free_x") +
	geom_hline(yintercept = 0.5, colour = "black", linetype = "dotted") +
	stat_slab(colour = "white", fill = "grey", alpha = 0.75,
			  position = position_nudge(x = 0.3)) +
	geom_boxplot(width = 0.15, size = 1, colour = "black",
				 fill = "white", outlier.colour = NA,
				 position = position_nudge(x = 0.3)) +
	geom_jitter(shape = 1, stroke = 1, width = 0.15, alpha = 0.5, size = 2) +
	geom_text(data = sample_size_lp,
			  aes(x = 1.5, y = 0,  label = paste0("N = ", n), group = lp),
			  colour = "black", show.legend = FALSE, 
			  position = position_dodge(width = 2), inherit.aes = FALSE) +
	labs(y = "Receptive vocabulary", 
		 colour = "Imputed", 
		 fill = "Imputed") +
	scale_y_continuous(limits = c(0, 1), labels = percent) +
	theme(legend.position = "top", 
		  legend.title = element_blank(),
		  panel.grid.major.x = element_blank(),
		  axis.title.x = element_blank(),
		  axis.text = element_text(size = 9))
```

@@

```{r}
#| label: fig-prior-epred
#| fig-width: 9
#| fig-height: 6
nd <- tibble(time_bin = seq(0, 20, 0.1)) %>% 
	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)

@@

	cols_label(n_excluded = "Exc.",
			   n_valid = "Inc.",
			   freq_prime_mean_valid = "Inc.",
			   freq_prime_mean_excluded = "Exc.",
			   freq_target_mean_valid = "Inc.",
			   freq_target_mean_excluded = "Exc.",
			   familiarity_prime_mean_valid = "Inc.",
			   familiarity_prime_mean_excluded = "Exc.",
			   familiarity_target_mean_valid = "Inc.",
			   familiarity_target_mean_excluded = "Exc.") %>% 
	summary_rows(groups = TRUE,
				 columns = matches("freq_") ,
				 fns = list("Mean" = ~mean(.)), 
				 formatter = fmt_number,
				 decimals = 1) %>% 
	summary_rows(groups = TRUE,
				 columns = matches("familiarity_"), 
				 fns = list("Mean" = ~mean(.)),
				 formatter = fmt_number,
				 scale_by = 100,
				 decimals = 1) %>% 
	grand_summary_rows(columns = c(n_valid, n_excluded),
					   fns = list("N" = ~sum(.)),
					   formatter = fmt_number,
					   decimals = 0) %>% 
	grand_summary_rows(columns = matches("familiarity_"),
					   fns = list("Mean" = ~mean(.)),
					   formatter = fmt_number,
					   scale_by = 100,
					   decimals = 1) %>% 
	grand_summary_rows(columns = matches("freq_"),
					   fns = list("Mean" = ~mean(.)),
					   formatter = fmt_number,
					   decimals = 1) %>% 
	tab_style(cell_text(align = "center"),
			  cells_column_labels()) %>% 
	tab_style(cell_text(weight = "bold"),
			  list(cells_column_spanners(),
			  	 cells_grand_summary(),
			  	 cells_row_groups(),
			  	 cells_stub_grand_summary(),
			  	 cells_stub_summary())) %>% 
	tab_footnote("Included trials.", cells_column_labels(matches("_valid"))) %>% 
	tab_footnote("Excluded trials.", cells_column_labels(matches("_excluded")))
```

@@

```{r}
#| label: fig-descriptives-aggregated
#| fig-width: 10
#| fig-height: 6
df %>% 
	group_by(id, lp, trial_type, age_group) %>%
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(trial_type, prop, colour = trial_type, fill = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	geom_line(aes(group = id), alpha = 0.25) +
	stat_slab(side = "right", scale = 0.5) +
	geom_boxplot(width = 0.1, size = 0.75, fill = "white", colour = "black", outlier.colour = NA) +
	labs(x = "Trial type", y = "Proportion of target looking", colour = "Trial type", fill = "Trial type") +
	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
	theme(legend.position = "none")
```

@@

```{r}
#| label: fig-descriptives-time-course
#| fig-width: 12
#| fig-height: 8
df %>% 
	group_by(id, time_bin, lp, trial_type, age_group) %>%
	summarise(prop = mean(prop), .groups = "drop") %>% 
	ggplot(aes(time_bin, prop, colour = trial_type, fill = trial_type, shape = trial_type)) +
	facet_grid(lp~age_group) +
	geom_hline(yintercept = 0.5, size = 1, colour = "grey") +
	stat_summary(fun.data = mean_se, geom = "errorbar", width = 0.2) +
	stat_summary(fun = mean, geom = "point", size = 2) +
	stat_summary(fun = mean, geom = "line", size = 0.75) +
	labs(x = "Time bin (100 ms)", y = "Proportion of target looking",
		 colour = "Trial type", fill = "Trial type", shape = "Trial type") +
	scale_y_continuous(labels = ~percent(., accuracy = 1)) +
	scale_x_continuous(labels = function(x) format(x*100, big.mark = ",")) +
	theme(legend.position = "top",
		  legend.title = element_blank(),
		  panel.grid = element_line(linetype = "dotted", colour = "grey"),
		  panel.grid.major = element_line(colour = "grey", linetype = "dotted"))
```

@@

str_repl <- c(
	"b_Intercept" = "Base",
	"b_ot1" = "Base",
	"b_ot2" = "Base",
	"b_ot3" = "Base",
	"b_age_group21_25" = "Age [21-25]",
	"b_age_group25_30" = "Age [25-30]",
	"b_lpmon_bil" = "Group",
	"b_trial_typerelated_unrelated" = "Prime (R)",
	"b_trial_typecognate_noncognate" = "Prime (C)",

	"b_age_group21_25:lpmon_bil" = "Age [21-25] × Group",
	"b_age_group25_30:lpmon_bil" = "Age [25-30] × Group",
	"b_age_group21_25:trial_typerelated_unrelated" = "Age [21-25] × Prime (R)",
	"b_age_group21_25:trial_typecognate_noncognate" = "Age [21-25] × Prime (C)",
	"b_age_group25_30:trial_typerelated_unrelated" = "Age [25-30] × Prime (R)",
	"b_age_group25_30:trial_typecognate_noncognate" = "Age [25-30] × Prime (C)",
	"b_lpmon_bil:trial_typerelated_unrelated" = "Group × Prime (R)",
	"b_lpmon_bil:trial_typecognate_noncognate" = "Group × Prime (C)",

	"b_age_group21_25:lpmon_bil:trial_typerelated_unrelated" = "Age [21-25] × Group × Prime (R)",
	"b_age_group21_25:lpmon_bil:trial_typecognate_noncognate" = "Age [21-25] × Group × Prime (C)",
	"b_age_group25_30:lpmon_bil:trial_typerelated_unrelated" = "Age [25-30] × Group × Prime (R)",
	"b_age_group25_30:lpmon_bil:trial_typecognate_noncognate" = "Age [25-30] × Group × Prime (C)"
)

@@

```{r}
#| label: fig-posterior-epred
#| fig-width: 12
#| fig-height: 8
nd <- expand_grid(time_bin = seq(0, 20, 0.1),
				  age_group = levels(fit_1$data$age_group),
				  lp = levels(fit_2$data$lp),
				  trial_type = levels(fit_4$data$trial_type)) %>% 
	poly_add_columns(time_bin, degree = 3, prefix = "ot", scale_width = 1)
